Supplementary Information

### 2020-11-06 doc/manuscript/MEE_manuscript.Rmd
minor updates

![**Figure 2 | Example comparison of climate sensitivity derived via traditional methods (**a**) and our approach (**b-f**).** Example is for the sensitivity of 14 species at SCBI (codes given in Table S2) to potential evapotranspiration ($PET$). Panel (**a**) shows a matrix of Pearson correlations between ring-width index and monthly climate variables. Black rectangle represents the period selected by *climwin* as the most influential window. Panels (**b-d**) give statistics for time windows tested in *climwin*, where window open and close indicate months prior to current August, and cells across the lower diaganol indicate single-month tests (akin to panel **a**). Panels (**b**) and (**c**) give values of linear and quadratic terms for each time window, and (**d**) gives the $\Delta AIC$ for each. The time window with the minimum $\Delta AIC$ (0-3 months prior to August, or May-July; black circles), was identified as the optimal window. Panel (**e**) shows the correlation of individual-level residuals to PET, with the function fit in *climwin*. Finally, panel (**f**) shows GLS model output, where $PET$ was a candidate driver variable (along with $PPT$; $DBH$ not included in this model). Plotted are responses of species for which $PET$ was included in the top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are significant, dashed lines when only one term is significant, and dotted lines when neither is significant. Transparent ribbons indicate 95% confidence intervals.](tables_figures/quilt_comparison.png)

@@

>>>>

![**Figure 2 | Example comparison of climate sensitivity derived via traditional methods (**a**) and our approach (**b-f**).** Example is for the sensitivity of 14 species at SCBI (codes given in Table S2) to potential evapotranspiration ($PET$). Panel (**a**) shows a matrix of Pearson correlations between ring-width index and monthly climate variables (using the chronologies of Helcoski et al. 2019). Black rectangle represents the period selected by *climwin* as the most influential window. Panels (**b-d**) give statistics for time windows tested in *climwin*, where window open and close indicate months prior to current August, and cells across the lower diaganol indicate single-month tests (akin to panel **a**). Panels (**b**) and (**c**) give values of linear and quadratic terms for each time window, and (**d**) gives the $\Delta AIC$ for each. The time window with the minimum $\Delta AIC$ (0-3 months prior to August, or May-July; black circles), was identified as the optimal window. Panel (**e**) shows the correlation of individual-level residuals to PET, with the function fit in *climwin*. Finally, panel (**f**) shows GLS model output, where $PET$ was a candidate driver variable (along with $PPT$; $DBH$ not included in this model). Plotted are responses of species for which $PET$ was included in the top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are significant, dashed lines when only one term is significant, and dotted lines when neither is significant. Transparent ribbons indicate 95% confidence intervals.](tables_figures/quilt_comparison.png)

@@

@forrester_does_2021 clarifies that $\Delta AGB$ increases with size across census data, but often declines with size over the course of a tree's life.
